Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/qrr.tex

Conceptually, a QRM is the data structure that models the question answering process.  Each QRM contains an ontilogical realm, an SSQ, and information to support the query answering process.  The realm may be one or more descriptive categories and is used for classification of the QRMs.  The SSQ describes the set of possible input and output categories from the associated natural language query.  The possible set of phrase inputs and outputs are grouped into contextual bins labeled \emph{who}, \emph{what}, \emph{when} and \emph{where}.  The ontilogical realm and the SSQ parameters act as a signature for the QRM object, analogous to a function signature.   The ontological representation of the SSQ is described in section {{XXX}}.

Additionally, the QRM contains representations for every page visited and the order of visitation.  For each page, we store the list of inputs to the URL such as form inputs and the possible outputs (highlighted portions of the webpage).  There is a mapping between the SSQ inputs and outputs used on any page to the specific page input.  Finally, there is a structure with mappings to the user inputs or outputs that are displayed to the user as answers.

@@

A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ \footnote{It is important to not that both $\Upsilon$ and $\Omega$ make up the SSQ structure.} such that:

\begin{enumerate}
%%%%%%%%%%%%%%% Separate the first 2 points as descriptions of the SSQ. --------------
\item $\Upsilon$ is the sequence of input categories $\left<
  \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$
  where $\Upsilon_{1}$ represents the \emph{who} context of the
  associated query, $\Upsilon_{2}$ represents the \emph{what} context,
  $\Upsilon_{3}$ represents the \emph{when} context, and
  $\Upsilon_{4}$ represents the \emph{where} context.

\item $\Omega$ is the sequence of output categories $\left<\Omega_{1},
  \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$
  represents the \emph{who} context of the associated query,
  $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
  represents the \emph{when} context, and $\Omega_{4}$ represents the
  \emph{where} context.

>>>>

Conceptually, a QRM is the data structure that models the question
answering process.  Each QRM contains an ontological realm, an SSQ,
and information to support the query answering process.  The realm may
be one or more descriptive categories and is used for classification
of the QRMs.  The SSQ describes the set of possible input and output
categories from the associated natural language query.  The possible
set of phrase inputs and outputs are grouped into contextual bins
labeled \emph{who}, \emph{what}, \emph{when} and \emph{where}.  The
ontological realm and the SSQ parameters act as a signature for the
QRM object, analogous to a function signature.  The ontological
representation of the SSQ is described in section \ref{sec:ssq}.

Additionally, the QRM contains representations for every page visited
and the order of visitation.  For each page, we store the list of
inputs to the URL such as form inputs and the possible outputs
(highlighted portions of the web page).  There is a mapping between the
SSQ inputs and outputs used on any page to the specific page input.
Finally, there is a structure with mappings to the user inputs or
outputs that are displayed to the user as answers.

@@

A QRM is a 4-tuple $Z = \left< \Sigma, P, M, A
\right>$ with the following structure:

\begin{enumerate}
%%%%%%%%%%%%%%% Separate the first 2 points as descriptions of the SSQ. --------------

\item $\Sigma = ( R, \Upsilon, \Omega )$ is the SSQ associated with the QRM.

  $R$ is the ontological realm associated with the QRM.

  $\Upsilon$ is the sequence of input categories drawn from $R$
  $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4}
  \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of
  the associated query, $\Upsilon_{2}$ represents the \emph{what}
  context, $\Upsilon_{3}$ represents the \emph{when} context, and
  $\Upsilon_{4}$ represents the \emph{where} context.

  $\Omega$ is the sequence of output categories drawn from $R$
  $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where
  $\Omega_{1}$ represents the \emph{who} context of the associated
  query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
  represents the \emph{when} context, and $\Omega_{4}$ represents the
  \emph{where} context.
